\setpath{Berserker}{000000}{C8000F}

\card[%
    name={Bloodthirsty Axe},
    cost={SA},
    text={%
        \attack{2}

        I get +2 attack power if you are being attacked.
    },
]

\card[%
    name={Battle Rage},
    cost={},
    permanent,
    text={%
        At the start of each turn, if your opponent has scored at least two 
        points you may play an additional action this turn.
    },
    % path={Berserker},
    % color-left=000000,
    % color-right=C8000F,
]

\card[%
    name={Rite of Scars},
    cost={},
    text={%
        \attack{2}

        In addition, you also attack yourself for the same amount.
        \textit{(Your opponent scores the points.)}

        Gain two Spirit.
    },
]

\card[%
    name={Pillage},
    cost={},
    text={%
        Banish a card your opponent played this turn.
    },
]


\card[%
    name={Retribution},
    cost={SAA},
    text={%
        \attack{2}

        I get +1 attack power for each two points your opponent has scored this match.

        I can't be blocked unless your opponent pays Any.
    },
]


\setpath{Druid}{00DB1D}{BF00FF}
\card[%
    name={Bind in Thorns},
    cost={WA},
    text={%
        \attack{1}

        \block
    },
]

\setpath{Fireheart}{F44B02}{F9028A}
\newcommand{\burn}[1]{\textcolor[HTML]{F22643}{\textbf{#1}}}

\card[%
    name={Insatiable Flame},
    cost={W},
    text={%
        \attack{1}

        I \burn{burn} your opponent when I hit. \textit{(This can help you set them ablaze)}
    },
]

\card[%
    name={Set Ablaze},
    cost={WWA},
    oneshot,
    text={%
        I cost no resources once your opponent has been \burn{burned} twice.
    
        \attack{4}
    },
]

\card[%
    name={Inferno Circle},
    cost={},
    sequence,
    text={%
        \sequence
        [If your opponent attacked this turn, I \burn{burn} them.]
        [If your opponent attacked this turn, I \burn{burn} them.]
    },
]

\card[%
    name={Kindled Flame},
    cost={},
    innate,
    permanent,
    text={%
        When your opponent is \burn{burned} for the third time play Set Ablaze immediately as a special action. If it is banished or forgotten, recall it first.
    },
]

\card[%
    name={Pyre Offering},
    cost={},
    sequence,
    oneshot,
    text={%
        \sequence
        [Banish a non-Fireheart card from your hand to recall Consumed by Flame.]
        [You may play an additional action]
    },
]

\card[%
    name={Consumed by Flame},
    cost={},
    extra,
    text={%
        \textit{This card begins the match forgotten and is recalled by Pyre Offering}

        Consumed by Flame is a copy of the card that was banished by Pyre Offering, except that it \burn{burns} your opponent when it hits and when it blocks their attacks.
    },
]


\setpath{Legionnaire}{FFA500}{AF0301}

\card[%
    name={Balanced Blade},
    cost={A},
    text={%
        \attack{2}

        Recall Parry.
    },
]

\card[%
    name={Parry},
    cost={A},
    extra,
    oneshot,
    text={%
        \textit{This card begins the match forgotten and is recalled by Balanced Blade.}

        I cost one resource less if you played Balanced Blade last turn.
        
        \block
    },
]

\card[%
    name={Arrow Volley},
    cost={SF},
    text={%
        Repeat the following twice:
        \attack{1}
        
        \textit{(One block can only stop one attack.)}
    },
]

\card[%
    name={Decisive Strike},
    cost={SAA},
    text={%
        I cost one resource less for each two points you've scored this match.
        
        \attack{3}
    },
]

\card[%
    name={Battle Tactics},
    cost={F},
    innate,
    permanent,
    text={%
        Choose a strategy:

        \textit{Skirmish} -- You may play an additional action on the second turn.

        \textit{Ambush} -- The first time you attack, give an attack +2 attack power.

        \textit{Besiege} -- Your opponent pays {Any}.
    },
]

\card[%
    name={Shield Wall},
    cost={S},
    permanent,
    text={%
        First turn:
        \block

        Whenever you play an attack, block an attack with less attack power.
    },
]


\setpath{Dancer}{5EF285}{F48DD2}

\card[%
    name={Elegant Reversal},
    cost={SF},
    text={%
        \block

        When I block an attack, I attack back with equal attack power.
    },
]

\card[%
    name={Mesmerize},
    cost={},
    sequence,
    text={%
        \sequence
            [No effect]
            [Your opponent's actions cost twice as many resources. \textit{(For example, an action that would cost {S}{A} costs {S}{S}{A}{A}.)}]
    },
]

\card[%
    name={Dizzying Spin},
    cost={F},
    sequence,
    text={%
        \sequence
            [\attack{1}\par If I hit, name a card.]
            [Your opponent can't play the named card(s).]
    },
]

\card[%
    name={Just Out of Reach},
    cost={A},
    text={%
        Your opponent's attacks get -2 attack power this turn.
    },
]

\card[%
    name={Entice to Dance},
    cost={A},
    innate,
    permanent,
    text={%
        Your opponent recalls Try to Keep Up.
        
        When the match ends, score three points unless your opponent has played Try to Keep Up.
    },
]

\card[%
    name={Try to Keep Up},
    cost={},
    extra,
    text={%
        \textit{This card begins the match forgotten and is given to your opponent by Entice to Dance.}

        Banish Try to Keep Up on top of Entice to Dance.
    },
]


\setpath{Arcanist}{E100FF}{5300EF}

\card[%
    name={Arcane Research},
    cost={F},
    text={%
        Choose two random advanced cards you have not yet learned and recall them. If you recall an innate card, play it immediately.
    },
]

\card[%
    name={Forcefield},
    cost={W},
    text={%
        \block

        For the rest of the match, Forcefield costs no resources.
    },
]

\card[%
    name={Meteor Invocation},
    cost={WA},
    sequence,
    text={%
        \sequence
            [No effect.]
            [\attack{4}]
    },
]

\card[%
    name={Shrinking Ray},
    cost={WA},
    oneshot,
    text={%
        Your opponent pays {Any}{Any} if able, or {Any} if that's all they have. They must undo an action they played this turn if doing so would make them more able to pay. \textit{(Undone actions are recalled and refunded and have no effect.)}
    },
]

\card[%
    name={Spellweaving},
    cost={},
    innate,
    permanent,
    text={%
        Reveal an Arcanist card and a non-Arcanist card from your hand. When you play one of those cards, play the other as a special action if able.
    },
]

\card[%
    name={All-Consuming Void},
    cost={A},
    extra,
    text={%
        \textit{Forbidden Magic - This card begins the match forgotten and can be recalled by an upgraded Arcane Research.}

        At end of turn, end the match. \textit{(The player with more points wins)}
    },
]

\card[%
    name={True Reincarnation},
    cost={},
    extra,
    text={%
        \textit{Forbidden Magic - This card begins the match forgotten and can be recalled by an upgraded Arcane Research.}

        If your opponent would score points this turn, instead they score no points and your resources are restored to your starting resources.
    },
]

\card[%
    name={Awaken the Old Gods},
    cost={AAA},
    extra,
    sequence,
    text={%
        \textit{Forbidden Magic - This card begins the match forgotten and can be recalled by an upgraded Arcane Research.}

        \sequence
            [\attack{4}]
            [\attack{4}]
    },
]

\card[%
    name={FAKE TEST CARD},
    cost={AAA},
    extra,
    oneshot,
    text={%
        \textit{Forbidden Magic - This card begins the match forgotten and can be recalled by an upgraded Arcane Research.}

        \attack{4}

        \attack{4}
    },
]

\card[%
    name={FAKE TEST CARD},
    cost={AAA},
    extra,
    oneshot,
    text={%
        \textit{Forbidden Magic - This card begins the match forgotten and can be recalled by an upgraded Arcane Research.}
        
        \sequence
            [\block]
            [\attack{4}]
    },
]






% \setpath{XXX}{aa00aa}{0000aa}
% \card[%
%     name={},
%     cost={},
%     text={%
%         
%     },
% ]
