\setpath{Arcanist}{E100FF}{5300EF}

\card[%
    name={Arcane Research},
    cost={F},
    text={%
        Choose \upgrade{two random advanced}{one random forbidden magic and one random advanced card} \upgrade{cards}{} you have not yet learned and recall them. If you recall an innate card, play it immediately.
    },
    upgrade cost={5},
    % upgrade={},
]

\card[%
    name={Forcefield},
    cost={W},
    text={%
        \block

        For the rest of the match, Forcefield costs no resources.
    },
]

\card[%
    name={Meteor Invocation},
    cost={WA},
    sequence,
    text={%
        \sequence
            [No effect.]
            [\attack{4}]
    },
    purchase={2},
    upgrade cost={5},
    upgrade={+2 attack power.},
]

\card[%
    name={Shrinking Ray},
    cost={WA},
    oneshot,
    text={%
        Your opponent pays \mana{AA} if able, or \mana{A} if that's all they have. They must undo an action they played this turn if doing so would make them more able to pay. \textit{(Undone actions are recalled and refunded and have no effect.)}
    },
    purchase={5},
]

\card[%
    name={Spellweaving},
    cost={},
    innate,
    permanent,
    text={%
        Reveal an Arcanist card and a non-Arcanist card from your hand. 
        
        For the rest of the match, when you play one of those cards, play the other as a special action if able.
    },
    purchase={8},
]

\card[%
    name={All-Consuming Void},
    cost={A},
    linked={an upgraded Arcane Research},
    linked type={Forbidden Magic},
    text={%
        At end of turn, end the match. \textit{(The player with more points wins)}
    },
]

\card[%
    name={True Reincarnation},
    cost={},
    linked={an upgraded Arcane Research},
    linked type={Forbidden Magic},
    oneshot,
    text={%
        If your opponent would score points this turn, instead they score no points and your resources are restored to your starting resources.
    },
]

\card[%
    name={Awaken the Old Gods},
    cost={AAA},
    linked={an upgraded Arcane Research},
    linked type={Forbidden Magic},
    sequence,
    text={%
        \sequence
            [\attack{4}]
            [\attack{4}]
    },
]
