\setpath{Assassin}{000000}{FF00AF}

\card[%
    name={Backstab},
    cost={F},
    text={%
        If your opponent isn't attacking: 

        \attack{3}
    },
]

\card[%
    name={Shadowstep},
    cost={},
    text={%
        \block
        
        Banish me unless you pay \mana{F}.
    },
]

\card[%
    name={Trap Setting},
    cost={F},
    text={%
        Secretly choose a Trap and put it into play face down.
        You can turn that card face up to play it as a special action any time after this turn ends.
    },
]

\newcommand{\traptext}{\textit{Trap - This card begins the match forgotten and is put into play by Trap Setting.}}

\card[%
    name={Poisoned Dagger},
    cost={},
    extra,
    text={%
        \traptext

        If you hit with an attack this turn, I become permanent and at the start of each turn, you score one point. Otherwise, banish me.
    },
]

\card[%
    name={Smoke Shroud},
    cost={},
    extra,
    oneshot,
    text={%
        \traptext
        
        If your opponent didn't attack last turn, they can't score points this turn.
    },
]

\card[%
    name={Feign Defeat},
    cost={},
    extra,
    oneshot,
    text={%
        \traptext

        If your opponent has more points than you, they can't block this turn.
    },
]

\card[%
    name={Always More Knives},
    cost={FAA},
    sequence,
    text={%
        \sequence
            [\attack{3}]
            [\attack{1}]
    },
]

\card[%
    name={Hidden in Plain Sight},
    cost={},
    innate,
    permanent,
    text={%
        After the first turn of the match, but before the second, there is a secret turn. Your opponent and their cards do not participate in this turn, and no points can be scored.
    },
]
