\setpath{Dancer}{5EF285}{F48DD2}

\card[%
    name={Elegant Reversal},
    cost={SF},
    text={%
        \block

        When I block an attack, I attack back with equal attack power.
    },
]

\card[%
    name={Mesmerize},
    cost={},
    sequence,
    text={%
        \sequence
            [\upgrade{No effect}]
            [Your opponent's actions cost twice as many resources. 
            
            \textit{(For example, an action that would cost \mana{FAA} costs \mana{FFAA}.)}]
    },
    upgrade cost={4},
    upgrade={\{Gain \mana{X}.\}},
]

\card[%
    name={Dizzying Spin},
    cost={F},
    sequence,
    text={%
        \sequence
            [\attack{1}\par \upgrade{If I hit}, name a card.]
            [Your opponent can't play the named card(s).]
    },
    purchase={0},
    upgrade cost={3},
    upgrade={\{Whether or not I hit\}},
]

\card[%
    name={Just Out of Reach},
    cost={A},
    text={%
        Your opponent's attacks get -2 attack power this turn.
    },
    purchase={0},
    upgrade cost={6},
    upgrade={Once per match you may play me any time as a special action. If you do, banish me after use.},
]

\card[%
    name={Entice to Dance},
    cost={A},
    innate,
    permanent,
    text={%
        Your opponent recalls Try to Keep Up.
        
        When the match ends, score three points unless your opponent has played Try to Keep Up.
    },
    purchase={3},
    upgrade cost={3},
    upgrade={Try to Keep Up costs \mana{A}.},
]

\card[%
    name={Try to Keep Up},
    cost={},
    extra,
    text={%
        \textit{This card begins the match forgotten and is given to your opponent by Entice to Dance.}

        Banish Try to Keep Up on top of Entice to Dance.

        \textit{(If Entice to Dance is upgraded, this card costs \mana{A}.)}
    },
]
