\setpath{Fireheart}{F44B02}{F9028A}
\newcommand{\burn}[1]{\textcolor[HTML]{F22643}{\textbf{#1}}}

\card[%
    name={Insatiable Flame},
    cost={W},
    text={%
        \attack{1}

        I \burn{burn} your opponent when I hit. \textit{(This can help you set them ablaze)}
    },
    upgrade cost={5},
    upgrade={+1 attack power.},
]

\card[%
    name={Set Ablaze},
    cost={WWAAA},
    oneshot,
    text={%
        I cost no resources once your opponent has been \burn{burned} twice.
    
        \attack{4}

        I can't be blocked.
    },
    upgrade cost={7},
    upgrade={Costs \mana{AA} less to cast.},
]

\card[%
    name={Inferno Circle},
    cost={},
    sequence,
    text={%
        \sequence
        [If your opponent attacked this turn, I \burn{burn} them.]
        [If your opponent attacked this turn, I \burn{burn} them.]
    },
    purchase={0},
    upgrade cost={4},
    upgrade={Repeats the same effect for a third turn.},
]

\card[%
    name={Kindled Flame},
    cost={},
    innate,
    permanent,
    text={%
        When your opponent is \burn{burned} for the third time play Set Ablaze immediately as a special action. If it is forgotten, recall it first.
    },
    purchase={3},
    upgrade cost={3},
    upgrade={Your opponent only needs to be burned twice instead of three times.},
]

\card[%
    name={Pyre Offering},
    cost={},
    sequence,
    oneshot,
    text={%
        \sequence
        [Banish a non-Fireheart card from your hand to recall Consumed by Flame.]
        [You may play an additional action.]
    },
    purchase={?},
]

\card[%
    name={Consumed by Flame},
    cost={},
    extra,
    text={%
        \textit{This card begins the match forgotten and is recalled by Pyre Offering}

        Consumed by Flame is a copy of the card that was banished by Pyre Offering, except that it \burn{burns} your opponent when it hits and when it blocks their attacks.
    },
]
